### 2012-07-15 docs/dissertation.tex
Docs

\documentclass[12pt,a4paper]{report}

\usepackage{epcc}
\usepackage{graphics}

% This example file shows how a thesis can be laid out using Latex. It
% does not use any special local features so should be portable to other
% places.
% 
% When producing draft copies of a thesis you may want to print only
% selected pages of the thesis. To do this use the command
% 
% dvips -f -p 4 -n 3 myfile.dvi | lpr
% 
% where -p 4 means start printing at page 4 (ie the page that will be
% numbered 4, not necessarily the 4th page) and -n 3 means print 3 pages.
% This example will print pages 4, 5 and 6.
% 
% If you want to print the thesis and also save paper you can print more
% than one page on each sheet of paper. Use the command
% 
% dvips -f myfile.dvi | psnup -2 | lpr
% 
% to print 2 pages per sheet. psnup can take values 2, 4, 8, or 9.
%
% To produce a PDF version you can create a PostScript copy first
%
% dvips -f myfile.dvi > myfile.pdf
%
% and then convert it
%
% distill myfile.ps
%
% or you can go straight to PDF
%
% pdflatex myfile
%
% Note that pdflatex expects all included figures to be in PDF too. See
% the includegraphics command below.

% This document contains many cross-references and forward references,
% eg in constructing a table of contents, so Latex may need to be run
% twice to get all the references correct. If you need to run Latex twice
% you may get the warning:
% 
% LaTeX Warning: Label(s) may have changed. Rerun to get cross-refSerences right.

% the following 4 lines are the content of the smallmargins.sty file
% but including them explicitly makes this more portable.
%AC%\oddsidemargin=0.1in
%AC%\topmargin=-0.5in
%AC%\textheight=9in
%AC%\textwidth=6.25in

%AC%\parskip 10pt
%AC%\parindent 0in

\begin{document}

%AC%\pagestyle{myheadings}
%AC%\markright{D.~S.~Henty}

%\title{A Latex thesis example}
%\author{D.~S.~Henty}
%\date{\today}

%\maketitle

\pagenumbering{roman}

\title{Title of Dissertation}
\author{Author's Name}
\date{\today}

\makeEPCCtitle

\thispagestyle{empty}

\vspace{12cm}

\begin{center}

\large{MSc in High Performance Computing}

\large{The University of Edinburgh}

\large{Year of Presentation: 2007}

\end{center}

\newpage

\begin{abstract}
This is the bit where you summarise what is in your thesis.
\end{abstract}

\pagenumbering{roman}

\tableofcontents
\listoftables
\listoffigures

\begin{titlepage}
\vspace*{2in}
% an acknowledgements section is completely optional but if you decide
% not to include it you should still include an empty {titlepage}
% environment as this initialises things like section and page numbering.
\section*{Acknowledgements}

This template is a slightly modified version of the one developed by
Prof. Charles Duncan for MSc students in the Dept. of Meteorology. His
acknowledgement follows:

{\em This template has been produced with help from many former students who
have shown different ways of doing things. Please make suggestions for
further improvements.}

\end{titlepage}

\pagenumbering{arabic}

\chapter{Introduction}
This should contain a description of your project and the problem you
are trying to solve. Where appropriate you should also include
references to work which has already been done on your topic and
anything else which lets you set your work in context.

One of the things you will need to do is to ensure that you have a
suitable list of references.  To do this you should see \cite{ref:lam}
or some other suitable reference.  Note the format of the citation used
here is the style favoured in this department.  Here is another
reference \cite{ref:bloggs} for good measure.

You will also want to make sure you have no spelling or grammatical
mistakes. To help idwentify spelling mistukes you caan use the commands
{\em ispell} or {\em spell}. See the appropriate manual pages. Remember
that spelling mistakes are not the only errors which can occur. Spelling
checkers will not find errors which are, in fact, valid words such as
{\em there} for {\em their}, nor will they find repeated words which
sometimes occur if your concentration is broken when typing. {\bf There
is no substitute for thorough proof reading!}

\chapter{Background theory}

\section{The easy bits}
This is just to show how to break things into sections.

Some paragraphs in this demonstration document are here to provide some
padding so that sections last for more than one page to illustrate what
happens on subsequent pages. Note that the page numbering style is usually
different on the first page of a new chapter than on subsequent pages.

Here is a padding paragraph.  Rhubarb.  More rhubarb.  Yet more rhubarb. 
Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet
more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb. 
More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more
rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More
rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb. 
Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet
more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb. 
More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more
rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.   Rhubarb.  More
rhubarb.  Yet more rhubarb.   Rhubarb.  More rhubarb.  Yet more
rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.    Rhubarb.  More
rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.

\section{The more difficult bits}
Some bits are hard.

Here is a padding paragraph.  Rhubarb.  More rhubarb.  Yet more rhubarb. 
Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet
more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb. 
More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more
rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More
rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb. 
Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet
more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb. 
More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more
rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.   Rhubarb.  More
rhubarb.  Yet more rhubarb.   Rhubarb.  More rhubarb.  Yet more
rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.    Rhubarb.  More
rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.

\subsection{Hard bits}
You might want to include an equation here:

\begin{equation} \delta N_{\nu} = (\delta N_{\nu})_{ex} + (\delta N_{\nu})_{au} 
\label{equation:delsplit}
% note that the label is optional but allows you to refer to this
% equation later.
\end{equation}

Here is a padding paragraph.  Rhubarb.  More rhubarb.  Yet more rhubarb. 
Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet
more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb. 
More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more
rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More
rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb. 
Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet
more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb. 
More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more
rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.   Rhubarb.  More
rhubarb.  Yet more rhubarb.   Rhubarb.  More rhubarb.  Yet more
rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.    Rhubarb.  More
rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.

Here is a padding paragraph.  Rhubarb.  More rhubarb.  Yet more rhubarb. 
Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet
more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb. 
More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more
rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More
rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb. 
Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet
more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb. 
More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more
rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.   Rhubarb.  More
rhubarb.  Yet more rhubarb.   Rhubarb.  More rhubarb.  Yet more
rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.    Rhubarb.  More
rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.

\subsection{Even harder bits}
This might be one of the places where you might want to refer to
equation \ref{equation:delsplit}. You will usually need to use the
Latex command twice to make cross-references like this work properly.
The cross-reference information is stored in the {\em .aux} file so don't
delete it.

\subsubsection{Numbering}
You can keep subdividing but eventually you get to a level where
numbering stops. This text is in a subsubsection which is not numbered
by default.

\paragraph{More on numbering:}

This text is in a paragraph which is also not numbered by default and
the ``title'' of the paragraph is not on a separate line.
If you want to increase the depth to which sections are numbered you
should see the section on setting the secnumdepth counter in the manual.

\chapter{Experimental design}

You might sometimes want to include equations without numbering them.

\begin{displaymath}
E=mc^{2}
\end{displaymath}

You might also want to include diagrams.  The example shows the use of
the special command which allows existing postscript files to be
included.  You would normally keep your figures separate from the text. 
These pictures might be satellite images or postscript output from some
program such as IDL, PV-WAVE, Uniras or xpaint.

Below I create a figure which is centred and stretched to 30\% of the
width of the page \verb+{0.30\hsize}+ and with the height stretched by
the same amount \verb+{!}+ to preserve the aspect ratio. If you omit the
extension (ie .eps, .ps or .pdf) on the file name then latex will pick
up the postscript copy whereas pdflatex will automatically pick up the
PDF version.

\begin{figure}

\begin{center}
\resizebox{0.30\hsize}{!}{\includegraphics{/usr/local/share/logos/eucrest}}
\end{center}

\caption{The University Crest}
\label{fig:eucrest}

\end{figure}

% see the man page for dvips for details of the special command which is
% much more powerful than is shown here. It allows offsets in the
% horizontal and vertical and scaling in x and y.

% choosing suitable values for offset and scale can be a tiring matter
% of trial and error.

% note that labels do not need to include a description of the object
% they are labelling but it can be helpful, eg \label{fig:figurename}.

You can use a label on a figure to refer to it later. The university
crest is in \ref{fig:eucrest}. Note that you should not use phrases like
``the figure above'' or ``the following figure'' since Latex may move
the figure relative to the text if it cannot be fitted onto the current page.

\chapter{Results and Analysis}

\section{Some results}
Here are some results.

\subsection{More results}
When showing results you are likely to use tables and graphs. You can
create tables easily in Latex.

\begin{table}[h]
\begin{center}
\begin{tabular}{||l|c|l||}
\hline
{\bf File names} & {\bf Satellite} & {\bf Resolution}\\
\hline
  worldr         &  Meteosat     &   5km\\
  worldg         &  Meteosat     &   5km\\
  worldb         &  Meteosat     &   5km\\
\hline
\end{tabular}
\end{center}
\caption{This is a simple table. More complicated tables can have
headings which pass over more than one column}
\label{simple_table}
\end{table}

If you want to produce fancier tables than shown in Table \ref{simple_table}
refer to the manual.

One of the simplest ways to produce simple graphs is to use gnuplot
which produces Latex output. Graph \ref{fig:gnu} was produced using
gnuplot with output designated as Latex so that a Latex output file is
produced which you can include directly or keep separate and refer to
using the {\em include} command.

Another approach is to draw simple figures using {\em xfig} which allows
you to export diagrams in Latex picture format so that the diagram can
be included directly.

Perhaps the most robust way to include graphs is to convert them to
PostScript or PDF and include them in the same was as was done in
Figure~\ref{fig:eucrest} for the University Crest. You can usually do
this with most packages, including Microsoft ones; one trick for
producing PostScript is to print to a dummy PostScript printer.

% in practice you would probably keep this in a separate file and use
% the \include{filename} command to insert it here.

\begin{figure}
% GNUPLOT: LaTeX picture
\setlength{\unitlength}{0.240900pt}
\ifx\plotpoint\undefined\newsavebox{\plotpoint}\fi
\sbox{\plotpoint}{\rule[-0.200pt]{0.400pt}{0.400pt}}%
\begin{picture}(1500,1200)(0,0)
\font\gnuplot=cmr10 at 10pt
\gnuplot
\sbox{\plotpoint}{\rule[-0.200pt]{0.400pt}{0.400pt}}%
\put(220.0,113.0){\rule[-0.200pt]{292.934pt}{0.400pt}}
\put(220.0,113.0){\rule[-0.200pt]{0.400pt}{245.477pt}}
\put(220.0,113.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(198,113){\makebox(0,0)[r]{$0$}}
\put(1416.0,113.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(220.0,317.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(198,317){\makebox(0,0)[r]{$0.2$}}
\put(1416.0,317.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(220.0,521.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(198,521){\makebox(0,0)[r]{$0.4$}}
\put(1416.0,521.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(220.0,724.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(198,724){\makebox(0,0)[r]{$0.6$}}
\put(1416.0,724.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(220.0,928.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(198,928){\makebox(0,0)[r]{$0.8$}}
\put(1416.0,928.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(220.0,1132.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(198,1132){\makebox(0,0)[r]{$1$}}
\put(1416.0,1132.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
\put(220.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(220,68){\makebox(0,0){$0$}}
\put(220.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(414.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(414,68){\makebox(0,0){$1$}}
\put(414.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(607.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(607,68){\makebox(0,0){$2$}}
\put(607.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(801.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(801,68){\makebox(0,0){$3$}}
\put(801.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(995.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(995,68){\makebox(0,0){$4$}}
\put(995.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(1188.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(1188,68){\makebox(0,0){$5$}}
\put(1188.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(1382.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(1382,68){\makebox(0,0){$6$}}
\put(1382.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
\put(220.0,113.0){\rule[-0.200pt]{292.934pt}{0.400pt}}
\put(1436.0,113.0){\rule[-0.200pt]{0.400pt}{245.477pt}}
\put(220.0,1132.0){\rule[-0.200pt]{292.934pt}{0.400pt}}
\put(45,622){\makebox(0,0){\shortstack{This is\\the\\$y$ axis}}}
\put(828,23){\makebox(0,0){This is the $x$ axis}}
\put(828,1177){\makebox(0,0){This is a plot of $y=sin(x)$}}
\put(220.0,113.0){\rule[-0.200pt]{0.400pt}{245.477pt}}
\sbox{\plotpoint}{\rule[-0.500pt]{1.000pt}{1.000pt}}%
\put(1306,1067){\makebox(0,0)[r]{sin(x)}}
\multiput(1328,1067)(20.756,0.000){4}{\usebox{\plotpoint}}
\put(1394,1067){\usebox{\plotpoint}}
\put(220,113){\usebox{\plotpoint}}
\multiput(220,113)(3.768,20.411){4}{\usebox{\plotpoint}}
\multiput(232,178)(4.132,20.340){3}{\usebox{\plotpoint}}
\multiput(245,242)(3.825,20.400){3}{\usebox{\plotpoint}}
\multiput(257,306)(3.884,20.389){3}{\usebox{\plotpoint}}
\multiput(269,369)(3.944,20.377){3}{\usebox{\plotpoint}}
\multiput(281,431)(4.326,20.300){3}{\usebox{\plotpoint}}
\multiput(294,492)(4.137,20.339){3}{\usebox{\plotpoint}}
\multiput(306,551)(4.276,20.310){3}{\usebox{\plotpoint}}
\multiput(318,608)(4.693,20.218){3}{\usebox{\plotpoint}}
\multiput(331,664)(4.583,20.243){2}{\usebox{\plotpoint}}
\multiput(343,717)(4.754,20.204){3}{\usebox{\plotpoint}}
\multiput(355,768)(5.034,20.136){2}{\usebox{\plotpoint}}
\multiput(367,816)(5.760,19.940){2}{\usebox{\plotpoint}}
\multiput(380,861)(5.579,19.992){3}{\usebox{\plotpoint}}
\put(398.00,923.50){\usebox{\plotpoint}}
\multiput(404,943)(7.049,19.522){2}{\usebox{\plotpoint}}
\multiput(417,979)(7.288,19.434){2}{\usebox{\plotpoint}}
\put(433.18,1021.10){\usebox{\plotpoint}}
\multiput(441,1040)(8.982,18.712){2}{\usebox{\plotpoint}}
\put(460.41,1076.97){\usebox{\plotpoint}}
\put(471.84,1094.28){\usebox{\plotpoint}}
\put(484.84,1110.41){\usebox{\plotpoint}}
\put(500.42,1124.01){\usebox{\plotpoint}}
\multiput(503,1126)(19.159,7.983){0}{\usebox{\plotpoint}}
\put(519.48,1131.37){\usebox{\plotpoint}}
\multiput(527,1132)(20.136,-5.034){0}{\usebox{\plotpoint}}
\put(539.74,1128.60){\usebox{\plotpoint}}
\put(557.04,1117.38){\usebox{\plotpoint}}
\put(570.79,1101.95){\usebox{\plotpoint}}
\put(582.44,1084.80){\usebox{\plotpoint}}
\put(593.09,1066.99){\usebox{\plotpoint}}
\multiput(601,1053)(8.430,-18.967){2}{\usebox{\plotpoint}}
\put(619.18,1010.54){\usebox{\plotpoint}}
\multiput(625,996)(7.413,-19.387){2}{\usebox{\plotpoint}}
\multiput(638,962)(6.403,-19.743){2}{\usebox{\plotpoint}}
\multiput(650,925)(5.830,-19.920){2}{\usebox{\plotpoint}}
\multiput(662,884)(5.461,-20.024){2}{\usebox{\plotpoint}}
\multiput(674,840)(5.533,-20.004){2}{\usebox{\plotpoint}}
\multiput(687,793)(4.937,-20.160){3}{\usebox{\plotpoint}}
\multiput(699,744)(4.667,-20.224){2}{\usebox{\plotpoint}}
\multiput(711,692)(4.858,-20.179){3}{\usebox{\plotpoint}}
\multiput(724,638)(4.276,-20.310){3}{\usebox{\plotpoint}}
\multiput(736,581)(4.205,-20.325){3}{\usebox{\plotpoint}}
\multiput(748,523)(4.070,-20.352){3}{\usebox{\plotpoint}}
\multiput(760,463)(4.326,-20.300){3}{\usebox{\plotpoint}}
\multiput(773,402)(3.884,-20.389){3}{\usebox{\plotpoint}}
\multiput(785,339)(3.884,-20.389){3}{\usebox{\plotpoint}}
\multiput(797,276)(4.070,-20.352){3}{\usebox{\plotpoint}}
\multiput(810,211)(3.825,-20.400){3}{\usebox{\plotpoint}}
\multiput(822,147)(3.607,-20.440){2}{\usebox{\plotpoint}}
\put(828,113){\usebox{\plotpoint}}
\end{picture}
\caption{Simple Gnuplot example}
\label{fig:gnu}
\end{figure}

\chapter{Conclusions}

This is the place to put your conclusions about your work. You can
split it into different sections if appropriate. You may want to include
a section of future work which could be carried out to continue your
research.

\appendix
% the appendix command just changes heading styles for appendices.

\chapter{Stuff which is too detailed}

Appendices should contain all the material which is considered too
detailed to be included in the main bod but which is, nevertheless,
important enough to be included in the thesis.

\chapter{Stuff which no-one will read}

Some people include in their thesis a lot of detail, particularly
computer code, which no-one will ever read. You should be careful that
anything like this you include should contain some element of uniqueness
which justifies its inclusion.

\begin{thebibliography}{100}

\bibitem{ref:lam} L.Lamport. {\em 1986 Latex User's Guide
and Reference Manual.} Addison Wesley. pp242.

\bibitem{ref:bloggs} F.Bloggs. {\em 1993 Latex Users do it
in Environments} Int. Journal of Silly Findings. pp 23-29.

\end{thebibliography}

\end{document}

### 2012-07-18 benchmark/md/util.c
Benchmark added

@@ -1,0 +1,23 @@
+#include <math.h>
+
+void visc_force(int N,double *f, double visc, double *vel)
+{
+  int i;
+          for(i=0;i<N;i++){
+            f[i] = -visc * vel[i];
+          }
+}
+void add_norm(int N,double *r, double *delta)
+{
+  int k;
+        for(k=0;k<N;k++){
+          *r += (delta[k] * delta[k]);
+        }
+}
+
+double force(double W, double delta, double r){
+  return W*delta/(double)(r*r*r);
+}
+
+
+

### 2012-07-18 environment/manager.py

@@ -3,7 +3,20 @@ import boto
 import subprocess
 import time
 import sys
+import os
 from optparse import OptionParser
+
+#Validate the input parameters
+def validate():
+	print "Hawki>>> Validating the inputs"
+	if not os.path.exists(results):
+    		os.makedirs(results)
+		print "Default results folder created"
+
+	if not os.path.exist(benchmark):
+		print "Benchmark folder doesn't exist"
+		sys.exit()
+
 
 #Set cluster parameters and cluster name
 def parseOptions():
@@ -16,7 +29,7 @@ def parseOptions():
                           help="Type of instance (string) [eg: m1.small]")
 	parser.add_option("-s",dest="size", type="int", default="2",
 	                  help="Cluster Size (int)")
-	parser.add_option("-b", dest="benchmark",  default="benchmark", 
+	parser.add_option("-b", dest="benchmark",  default="../benchmark", 
                   	  help="Path to benchmark code and scripts (folder)", metavar="FILE")
 	parser.add_option("-u",dest="username", type="string", default="sgeadmin",
 	                  help="Cluster login Username (string)")
@@ -41,6 +54,7 @@ def startCluster():
 		   print "Front node :"+hostname
 	except StandardError, err:
         	print err
+		terminateCluster()
 		sys.exit()
 
 
@@ -61,6 +75,7 @@ def transferFiles():
 		print output
 	except StandardError, err: #clean up
         	print err
+		terminateCluster()
 		sys.exit()
 	
 #ssh frontend pem and run scripts waiting for results
@@ -75,6 +90,7 @@ def runBenchmark():
 		print output
 	except StandardError, err:
 	        print err
+		terminateCluster()
 	        sys.exit()
 
 
@@ -91,6 +107,7 @@ def getResults():
 
 	except StandardError, err:
 	        print err
+		terminateCluster()
 		sys.exit()
 
 

### 2012-07-18 docs/dissertation/MSc-coursework.tex
dissertation template

--- 2012-07-15 docs/dissertation.tex
@@
-\documentclass[12pt,a4paper]{report}
+\documentclass[12pt,a4paper]{article}
 
@@
 
-% the following 4 lines are the content of the smallmargins.sty file
-% but including them explicitly makes this more portable.
-%AC%\oddsidemargin=0.1in
-%AC%\topmargin=-0.5in
-%AC%\textheight=9in
-%AC%\textwidth=6.25in
-
-%AC%\parskip 10pt
-%AC%\parindent 0in
-
 \begin{document}
 
-%AC%\pagestyle{myheadings}
-%AC%\markright{D.~S.~Henty}
-
-%\title{A Latex thesis example}
-%\author{D.~S.~Henty}
-%\date{\today}
-
-%\maketitle
-
-\pagenumbering{roman}
-
-\title{Title of Dissertation}
-\author{Author's Name}
+\title{A Latex Coursework Example}
+\author{David Henty}
 \date{\today}
@@
 
-\vspace{12cm}
-
-\begin{center}
-
-\large{MSc in High Performance Computing}
-
-\large{The University of Edinburgh}
-
-\large{Year of Presentation: 2007}
-
-\end{center}
-
 \newpage
-
-\begin{abstract}
-This is the bit where you summarise what is in your thesis.
-\end{abstract}
 
@@
 \tableofcontents
-\listoftables
-\listoffigures
 
-\begin{titlepage}
-\vspace*{2in}
-% an acknowledgements section is completely optional but if you decide
-% not to include it you should still include an empty {titlepage}
-% environment as this initialises things like section and page numbering.
+\newpage
+
 \section*{Acknowledgements}
@@
 
-\end{titlepage}
+\section*{Note}
 
+This template was originally created for a full MSc dissertation.
+Although I have modified the format slightly (eg there are no separate
+chapters), I have not substantially changed the text or the advice
+appearing in the \LaTeX comments (source lines beginning with \%). You
+should therefore be aware that for a short piece of coursework you may
+not need to go into as much detail as indicated here. For example, you
+might not need to include any acknowledgements and any reference list is
+likely to be very short.
+
+\newpage
 \pagenumbering{arabic}
 
-\chapter{Introduction}
+\section{Introduction}
+
 This should contain a description of your project and the problem you
@@
 
-\chapter{Background theory}
-
-\section{The easy bits}
+\subsection{The easy bits}
 This is just to show how to break things into sections.
@@
 
-\section{The more difficult bits}
+\subsection{The more difficult bits}
 Some bits are hard.
@@
 
-\subsection{Hard bits}
+\subsubsection{Hard bits}
 You might want to include an equation here:
@@
 
-\subsection{Even harder bits}
+\subsubsection{Even harder bits}
 This might be one of the places where you might want to refer to
@@
 
-\subsubsection{Numbering}
-You can keep subdividing but eventually you get to a level where
-numbering stops. This text is in a subsubsection which is not numbered
-by default.
-
 \paragraph{More on numbering:}
@@
 the ``title'' of the paragraph is not on a separate line.
-If you want to increase the depth to which sections are numbered you
-should see the section on setting the secnumdepth counter in the manual.
+If you want to increase the depth to which subsections are numbered you
+should see the subsection on setting the secnumdepth counter in the manual.
 
-\chapter{Experimental design}
+\section{Experimental design}
 
@@
 \begin{center}
-\resizebox{0.30\hsize}{!}{\includegraphics{/usr/local/share/logos/eucrest}}
+\resizebox{0.30\hsize}{!}{\includegraphics{logos/eucrest}}
 \end{center}
@@
 
-\chapter{Results and Analysis}
+\section{Results and Analysis}
 
-\section{Some results}
+\subsection{Some results}
 Here are some results.
 
-\subsection{More results}
+\subsubsection{More results}
 When showing results you are likely to use tables and graphs. You can
@@
 
-One of the simplest ways to produce simple graphs is to use gnuplot
-which produces Latex output. Graph \ref{fig:gnu} was produced using
-gnuplot with output designated as Latex so that a Latex output file is
-produced which you can include directly or keep separate and refer to
-using the {\em include} command.
+One way to produce simple graphs is to use gnuplot which can produce
+native Latex output. Graph \ref{fig:gnu} was produced using gnuplot with
+output designated as Latex; this creates a Latex output file which you
+can include directly or keep separate and refer to using the {\em
+include} command.
 
@@
 
-Perhaps the most robust way to include graphs is to convert them to
-PostScript or PDF and include them in the same was as was done in
+Perhaps the most robust way to include graphs is to create then using
+whatever package you like (eg Excel) and then convert them to PostScript
+or PDF and include them in the same was as was done in
 Figure~\ref{fig:eucrest} for the University Crest. You can usually do
-this with most packages, including Microsoft ones; one trick for
-producing PostScript is to print to a dummy PostScript printer.
+this with most packages, including Microsoft ones. One trick for
+producing PostScript is to print to a dummy PostScript printer; for PDF
+you can use the free CutePDF utilities at {\verb+www.cutepdf.com+}.
 
@@
 
-\chapter{Conclusions}
+\section{Conclusions}
 
 This is the place to put your conclusions about your work. You can
-split it into different sections if appropriate. You may want to include
-a section of future work which could be carried out to continue your
+split it into different subsections if appropriate. You may want to include
+a subsection of future work which could be carried out to continue your
 research.
-
-\appendix
-% the appendix command just changes heading styles for appendices.
-
-\chapter{Stuff which is too detailed}
-
-Appendices should contain all the material which is considered too
-detailed to be included in the main bod but which is, nevertheless,
-important enough to be included in the thesis.
-
-\chapter{Stuff which no-one will read}
-
-Some people include in their thesis a lot of detail, particularly
-computer code, which no-one will ever read. You should be careful that
-anything like this you include should contain some element of uniqueness
-which justifies its inclusion.
 

### 2012-07-18 environment/manager.py
dissertation template

@@ -66,7 +66,7 @@ def transferFiles():
 #ssh frontend pem and run scripts waiting for results
 #execute program  starcluster sshmaster --user sgeadmin pythoncluster ./instructions.sh
 def runBenchmark():
-	print ">>> Running Benchmark ..."
+	print "Hawki>>> Running Benchmark ..."
 	try:
 		process = subprocess.Popen("starcluster sshmaster --user "+username + " " + clustername +
 			" ./instructions.sh", shell=True, stdout=subprocess.PIPE, stderr=subprocess.STDOUT)

### 2012-07-21 docs/dissertation/MSc-coursework.tex
weekend commit

--- 2012-07-15 docs/dissertation.tex
@@
 
-\title{Title of Dissertation}
-\author{Author's Name}
+\title{Hawk-i HPC CLoud Benchmark Tool}
+\author{Visakh Muraleedharan}
 \date{\today}
@@
 
-\large{Year of Presentation: 2007}
+\large{Year of Presentation: 2012}
 
@@
 \begin{abstract}
-This is the bit where you summarise what is in your thesis.
+The switch to cloud computing significant advancement in the history of computing.
 \end{abstract}
@@
 
-This template is a slightly modified version of the one developed by
-Prof. Charles Duncan for MSc students in the Dept. of Meteorology. His
-acknowledgement follows:
-
-{\em This template has been produced with help from many former students who
-have shown different ways of doing things. Please make suggestions for
-further improvements.}
-
 \end{titlepage}
@@
 \chapter{Introduction}
-This should contain a description of your project and the problem you
-are trying to solve. Where appropriate you should also include
-references to work which has already been done on your topic and
-anything else which lets you set your work in context.
+Stating the problem and
 
-One of the things you will need to do is to ensure that you have a
-suitable list of references.  To do this you should see \cite{ref:lam}
-or some other suitable reference.  Note the format of the citation used
-here is the style favoured in this department.  Here is another
-reference \cite{ref:bloggs} for good measure.
+\chapter{Background}
 
-You will also want to make sure you have no spelling or grammatical
-mistakes. To help idwentify spelling mistukes you caan use the commands
-{\em ispell} or {\em spell}. See the appropriate manual pages. Remember
-that spelling mistakes are not the only errors which can occur. Spelling
-checkers will not find errors which are, in fact, valid words such as
-{\em there} for {\em their}, nor will they find repeated words which
-sometimes occur if your concentration is broken when typing. {\bf There
-is no substitute for thorough proof reading!}
+\section{Cloud Computing}
 
-\chapter{Background theory}
+\subsection{Why Cloud Computing?}
+\subsubsection{Resource on-demand}
+easy, accesibility
+\subsubsection{Pay as you go}
+\subsubsection{Maintenance and Upgradation}
+\subsubsection{Eco-friendly}
 
-\section{The easy bits}
-This is just to show how to break things into sections.
+\subsection{Cloud Computing service models}
+\subsubsection{IaaS}
+\subsubsection{PaaS}
+\subsubsection{Saas}
 
-Some paragraphs in this demonstration document are here to provide some
-padding so that sections last for more than one page to illustrate what
-happens on subsequent pages. Note that the page numbering style is usually
-different on the first page of a new chapter than on subsequent pages.
+\subsection{Cloud Computing Deployment models}
+\subsubsection{Private Cloud}
+\subsubsection{Public Cloud}
+\subsubsection{Hybrid Cloud}
+\subsubsection{Community Cloud}
 
-Here is a padding paragraph.  Rhubarb.  More rhubarb.  Yet more rhubarb. 
-Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet
-more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb. 
-More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more
-rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More
-rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb. 
-Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet
-more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb. 
-More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more
-rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.   Rhubarb.  More
-rhubarb.  Yet more rhubarb.   Rhubarb.  More rhubarb.  Yet more
-rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.    Rhubarb.  More
-rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.
+\section{Amazon Web Service}
+\subsection{Amazon Machine Instance}
+\subsection{Types of Instances}
+\subsection{Amazon EC2}
+different instances chart and limitations of microinstance.
+\subsubsection{EC2 cluster compute}
 
-\section{The more difficult bits}
-Some bits are hard.
+\section{HPC in the cloud}
+Introduction Paragraph, comparison with Clusters
+\subsection{Advantages}
+\subsection{Limitation}
+Network Limitations, Availability, Stability of performance
+Benifits
+\subsection{Amazon Cluster compute}
 
-Here is a padding paragraph.  Rhubarb.  More rhubarb.  Yet more rhubarb. 
-Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet
-more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb. 
-More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more
-rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More
-rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb. 
-Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet
-more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb. 
-More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more
-rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.   Rhubarb.  More
-rhubarb.  Yet more rhubarb.   Rhubarb.  More rhubarb.  Yet more
-rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.    Rhubarb.  More
-rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.
+\section{Parallel Applications and 13 Dwarfs}
+Explain the 13 dwarfs and under the two sections explain N-body and FFT
 
-\subsection{Hard bits}
-You might want to include an equation here:
+\subsection{N-Body Methods}
+MD, About the dwarf and application types
+optimisation, n^2 and nlogn
+Communication pattern!!!
 
-\begin{equation} \delta N_{\nu} = (\delta N_{\nu})_{ex} + (\delta N_{\nu})_{au} 
-\label{equation:delsplit}
-% note that the label is optional but allows you to refer to this
-% equation later.
-\end{equation}
+\subsection{Spectral Methods}
+In scientific computing, a class of techniques used to numerically solve differential equations involving the use of Fast Fouries Transform are called spectral methods
 
-Here is a padding paragraph.  Rhubarb.  More rhubarb.  Yet more rhubarb. 
-Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet
-more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb. 
-More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more
-rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More
-rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb. 
-Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet
-more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb. 
-More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more
-rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.   Rhubarb.  More
-rhubarb.  Yet more rhubarb.   Rhubarb.  More rhubarb.  Yet more
-rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.    Rhubarb.  More
-rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.
+Fourier transform
+Jean Baptiste Joseph Fourier (1768-1830) first employed what we now call Fourier transforms whilst working on the theory of heat 
+Linear transform which takes temporal or spatial information and converts into information which lies in the frequency domain
+Who would use Fourier Transforms? 
+• Physics 
+– Cosmology (P3M N-body solvers) 
+– Fluid mechanics 
+– Quantum physics 
+– Signal and image processing 
+– Antenna studies 
+– Optics
 
-Here is a padding paragraph.  Rhubarb.  More rhubarb.  Yet more rhubarb. 
-Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet
-more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb. 
-More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more
-rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More
-rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb. 
-Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet
-more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.  Rhubarb. 
-More rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more
-rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.   Rhubarb.  More
-rhubarb.  Yet more rhubarb.   Rhubarb.  More rhubarb.  Yet more
-rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.    Rhubarb.  More
-rhubarb.  Yet more rhubarb.  Rhubarb.  More rhubarb.  Yet more rhubarb.
+• Numerical analysis 
+– Linear systems analysis 
+– Boundary value problems 
+– Large integer multiplication (Prime finding)
 
-\subsection{Even harder bits}
-This might be one of the places where you might want to refer to
-equation \ref{equation:delsplit}. You will usually need to use the
-Latex command twice to make cross-references like this work properly.
-The cross-reference information is stored in the {\em .aux} file so don't
-delete it.
+• Statistics 
+– Random process modelling 
+– Probability theory
 
-\subsubsection{Numbering}
-You can keep subdividing but eventually you get to a level where
-numbering stops. This text is in a subsubsection which is not numbered
-by default.
+{\underline}Discrete Fourier Transform
+The discrete Fourier transform of N complex points fk is defined as 
+\begin{math}
 
-\paragraph{More on numbering:}
+\end{math}
 
-This text is in a paragraph which is also not numbered by default and
-the ``title'' of the paragraph is not on a separate line.
-If you want to increase the depth to which sections are numbered you
-should see the section on setting the secnumdepth counter in the manual.
+Communication pattern!!!
 
-\chapter{Experimental design}
+\chapter{Live Benchmark Tool Setup}
+\section{System Design}
+\subsection{Architecture}
+\subsection{Sequence diagram}
+\subsection{Database Design}
 
-You might sometimes want to include equations without numbering them.
-
-\begin{displaymath}
-E=mc^{2}
-\end{displaymath}
-
-You might also want to include diagrams.  The example shows the use of
-the special command which allows existing postscript files to be
-included.  You would normally keep your figures separate from the text. 
-These pictures might be satellite images or postscript output from some
-program such as IDL, PV-WAVE, Uniras or xpaint.
-
-Below I create a figure which is centred and stretched to 30\% of the
-width of the page \verb+{0.30\hsize}+ and with the height stretched by
-the same amount \verb+{!}+ to preserve the aspect ratio. If you omit the
-extension (ie .eps, .ps or .pdf) on the file name then latex will pick
-up the postscript copy whereas pdflatex will automatically pick up the
-PDF version.
-
-\begin{figure}
-
-\begin{center}
-\resizebox{0.30\hsize}{!}{\includegraphics{/usr/local/share/logos/eucrest}}
-\end{center}
-
-\caption{The University Crest}
-\label{fig:eucrest}
-
-\end{figure}
-
-% see the man page for dvips for details of the special command which is
-% much more powerful than is shown here. It allows offsets in the
-% horizontal and vertical and scaling in x and y.
-
-% choosing suitable values for offset and scale can be a tiring matter
-% of trial and error.
-
-% note that labels do not need to include a description of the object
-% they are labelling but it can be helpful, eg \label{fig:figurename}.
-
-You can use a label on a figure to refer to it later. The university
-crest is in \ref{fig:eucrest}. Note that you should not use phrases like
-``the figure above'' or ``the following figure'' since Latex may move
-the figure relative to the text if it cannot be fitted onto the current page.
+\section{Instance types Used}
+Refer to graph in Background
+Why these types?
+\section{Sun Grid Engine Cluster}
+Why sungrid Engine
+\section{SGE Clustering in Amazon cloud}
+  benchmark to show how cluster instances are faster than normal high cpu instances
+\section{Web interface}
+Describe in detail
+\subsection{Admin panel}
+\subsection{User Dashboard}
 
 \chapter{Results and Analysis}
+\section{Serial}
+for each instance type
+time to result, execution time, increasing problem size
+N-body and FFT
 
-\section{Some results}
-Here are some results.
-
-\subsection{More results}
-When showing results you are likely to use tables and graphs. You can
-create tables easily in Latex.
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}{||l|c|l||}
-\hline
-{\bf File names} & {\bf Satellite} & {\bf Resolution}\\
-\hline
-  worldr         &  Meteosat     &   5km\\
-  worldg         &  Meteosat     &   5km\\
-  worldb         &  Meteosat     &   5km\\
-\hline
-\end{tabular}
-\end{center}
-\caption{This is a simple table. More complicated tables can have
-headings which pass over more than one column}
-\label{simple_table}
-\end{table}
-
-If you want to produce fancier tables than shown in Table \ref{simple_table}
-refer to the manual.
-
-One of the simplest ways to produce simple graphs is to use gnuplot
-which produces Latex output. Graph \ref{fig:gnu} was produced using
-gnuplot with output designated as Latex so that a Latex output file is
-produced which you can include directly or keep separate and refer to
-using the {\em include} command.
-
-Another approach is to draw simple figures using {\em xfig} which allows
-you to export diagrams in Latex picture format so that the diagram can
-be included directly.
-
-Perhaps the most robust way to include graphs is to convert them to
-PostScript or PDF and include them in the same was as was done in
-Figure~\ref{fig:eucrest} for the University Crest. You can usually do
-this with most packages, including Microsoft ones; one trick for
-producing PostScript is to print to a dummy PostScript printer.
-
-% in practice you would probably keep this in a separate file and use
-% the \include{filename} command to insert it here.
-
-\begin{figure}
-% GNUPLOT: LaTeX picture
-\setlength{\unitlength}{0.240900pt}
-\ifx\plotpoint\undefined\newsavebox{\plotpoint}\fi
-\sbox{\plotpoint}{\rule[-0.200pt]{0.400pt}{0.400pt}}%
-\begin{picture}(1500,1200)(0,0)
-\font\gnuplot=cmr10 at 10pt
-\gnuplot
-\sbox{\plotpoint}{\rule[-0.200pt]{0.400pt}{0.400pt}}%
-\put(220.0,113.0){\rule[-0.200pt]{292.934pt}{0.400pt}}
-\put(220.0,113.0){\rule[-0.200pt]{0.400pt}{245.477pt}}
-\put(220.0,113.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(198,113){\makebox(0,0)[r]{$0$}}
-\put(1416.0,113.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(220.0,317.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(198,317){\makebox(0,0)[r]{$0.2$}}
-\put(1416.0,317.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(220.0,521.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(198,521){\makebox(0,0)[r]{$0.4$}}
-\put(1416.0,521.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(220.0,724.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(198,724){\makebox(0,0)[r]{$0.6$}}
-\put(1416.0,724.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(220.0,928.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(198,928){\makebox(0,0)[r]{$0.8$}}
-\put(1416.0,928.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(220.0,1132.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(198,1132){\makebox(0,0)[r]{$1$}}
-\put(1416.0,1132.0){\rule[-0.200pt]{4.818pt}{0.400pt}}
-\put(220.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(220,68){\makebox(0,0){$0$}}
-\put(220.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(414.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(414,68){\makebox(0,0){$1$}}
-\put(414.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(607.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(607,68){\makebox(0,0){$2$}}
-\put(607.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(801.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(801,68){\makebox(0,0){$3$}}
-\put(801.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(995.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(995,68){\makebox(0,0){$4$}}
-\put(995.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(1188.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(1188,68){\makebox(0,0){$5$}}
-\put(1188.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(1382.0,113.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(1382,68){\makebox(0,0){$6$}}
-\put(1382.0,1112.0){\rule[-0.200pt]{0.400pt}{4.818pt}}
-\put(220.0,113.0){\rule[-0.200pt]{292.934pt}{0.400pt}}
-\put(1436.0,113.0){\rule[-0.200pt]{0.400pt}{245.477pt}}
-\put(220.0,1132.0){\rule[-0.200pt]{292.934pt}{0.400pt}}
-\put(45,622){\makebox(0,0){\shortstack{This is\\the\\$y$ axis}}}
-\put(828,23){\makebox(0,0){This is the $x$ axis}}
-\put(828,1177){\makebox(0,0){This is a plot of $y=sin(x)$}}
-\put(220.0,113.0){\rule[-0.200pt]{0.400pt}{245.477pt}}
-\sbox{\plotpoint}{\rule[-0.500pt]{1.000pt}{1.000pt}}%
-\put(1306,1067){\makebox(0,0)[r]{sin(x)}}
-\multiput(1328,1067)(20.756,0.000){4}{\usebox{\plotpoint}}
-\put(1394,1067){\usebox{\plotpoint}}
-\put(220,113){\usebox{\plotpoint}}
-\multiput(220,113)(3.768,20.411){4}{\usebox{\plotpoint}}
-\multiput(232,178)(4.132,20.340){3}{\usebox{\plotpoint}}
-\multiput(245,242)(3.825,20.400){3}{\usebox{\plotpoint}}
-\multiput(257,306)(3.884,20.389){3}{\usebox{\plotpoint}}
-\multiput(269,369)(3.944,20.377){3}{\usebox{\plotpoint}}
-\multiput(281,431)(4.326,20.300){3}{\usebox{\plotpoint}}
-\multiput(294,492)(4.137,20.339){3}{\usebox{\plotpoint}}
-\multiput(306,551)(4.276,20.310){3}{\usebox{\plotpoint}}
-\multiput(318,608)(4.693,20.218){3}{\usebox{\plotpoint}}
-\multiput(331,664)(4.583,20.243){2}{\usebox{\plotpoint}}
-\multiput(343,717)(4.754,20.204){3}{\usebox{\plotpoint}}
-\multiput(355,768)(5.034,20.136){2}{\usebox{\plotpoint}}
-\multiput(367,816)(5.760,19.940){2}{\usebox{\plotpoint}}
-\multiput(380,861)(5.579,19.992){3}{\usebox{\plotpoint}}
-\put(398.00,923.50){\usebox{\plotpoint}}
-\multiput(404,943)(7.049,19.522){2}{\usebox{\plotpoint}}
-\multiput(417,979)(7.288,19.434){2}{\usebox{\plotpoint}}
-\put(433.18,1021.10){\usebox{\plotpoint}}
-\multiput(441,1040)(8.982,18.712){2}{\usebox{\plotpoint}}
-\put(460.41,1076.97){\usebox{\plotpoint}}
-\put(471.84,1094.28){\usebox{\plotpoint}}
-\put(484.84,1110.41){\usebox{\plotpoint}}
-\put(500.42,1124.01){\usebox{\plotpoint}}
-\multiput(503,1126)(19.159,7.983){0}{\usebox{\plotpoint}}
-\put(519.48,1131.37){\usebox{\plotpoint}}
-\multiput(527,1132)(20.136,-5.034){0}{\usebox{\plotpoint}}
-\put(539.74,1128.60){\usebox{\plotpoint}}
-\put(557.04,1117.38){\usebox{\plotpoint}}
-\put(570.79,1101.95){\usebox{\plotpoint}}
-\put(582.44,1084.80){\usebox{\plotpoint}}
-\put(593.09,1066.99){\usebox{\plotpoint}}
-\multiput(601,1053)(8.430,-18.967){2}{\usebox{\plotpoint}}
-\put(619.18,1010.54){\usebox{\plotpoint}}
-\multiput(625,996)(7.413,-19.387){2}{\usebox{\plotpoint}}
-\multiput(638,962)(6.403,-19.743){2}{\usebox{\plotpoint}}
-\multiput(650,925)(5.830,-19.920){2}{\usebox{\plotpoint}}
-\multiput(662,884)(5.461,-20.024){2}{\usebox{\plotpoint}}
-\multiput(674,840)(5.533,-20.004){2}{\usebox{\plotpoint}}
-\multiput(687,793)(4.937,-20.160){3}{\usebox{\plotpoint}}
-\multiput(699,744)(4.667,-20.224){2}{\usebox{\plotpoint}}
-\multiput(711,692)(4.858,-20.179){3}{\usebox{\plotpoint}}
-\multiput(724,638)(4.276,-20.310){3}{\usebox{\plotpoint}}
-\multiput(736,581)(4.205,-20.325){3}{\usebox{\plotpoint}}
-\multiput(748,523)(4.070,-20.352){3}{\usebox{\plotpoint}}
-\multiput(760,463)(4.326,-20.300){3}{\usebox{\plotpoint}}
-\multiput(773,402)(3.884,-20.389){3}{\usebox{\plotpoint}}
-\multiput(785,339)(3.884,-20.389){3}{\usebox{\plotpoint}}
-\multiput(797,276)(4.070,-20.352){3}{\usebox{\plotpoint}}
-\multiput(810,211)(3.825,-20.400){3}{\usebox{\plotpoint}}
-\multiput(822,147)(3.607,-20.440){2}{\usebox{\plotpoint}}
-\put(828,113){\usebox{\plotpoint}}
-\end{picture}
-\caption{Simple Gnuplot example}
-\label{fig:gnu}
-\end{figure}
+\section{Parallel program}
+execution time, increasing problem size, number of cores
+N-body and FFT
+\section{Stability of results}
+History of execution, snapshot from dashboard
 
 \chapter{Conclusions}
-
-This is the place to put your conclusions about your work. You can
-split it into different sections if appropriate. You may want to include
-a section of future work which could be carried out to continue your
-research.
 
@@
 
-\chapter{Stuff which is too detailed}
-
-Appendices should contain all the material which is considered too
-detailed to be included in the main bod but which is, nevertheless,
-important enough to be included in the thesis.
-
-\chapter{Stuff which no-one will read}
-
-Some people include in their thesis a lot of detail, particularly
-computer code, which no-one will ever read. You should be careful that
-anything like this you include should contain some element of uniqueness
-which justifies its inclusion.
+\chapter{Cluster Computing Setup}
+\subsection{Using Starcluster}
+\subsection{Cluster Management package}
+\subsection{Using Sun Grid Engine}
+\subsection{Creating Dashboard}
+\chapter{Benchmarking  programs}
 

### 2012-07-23 benchmark/fft/fft_benchmark.c
fft benchmark program

@@ -1,0 +1,115 @@
+/*----------------------------------------------
+   fft_test.c - demonstration program for fft.c
+  ----------------------------------------------*/
+
+/******************************************************************************
+ * This program demonstrates how to use the file fft.c to calculate an FFT    *
+ * of given time-domain samples, as well as to calculate an inverse FFT       *
+ * (IFFT) of given frequency-domain samples.  First, N complex-valued time-   *
+ * domain samples x, in rectangular form (Re x, Im x), are read from a        *
+ * specified file; the 2N values are assumed to be separated by whitespace.   *
+ * Then, an N-point FFT of these samples is found by calling the function     *
+ * fft, thereby yielding N complex-valued frequency-domain samples X in       *
+ * rectangular form (Re X, Im X).  Next, an N-point IFFT of these samples is  *
+ * is found by calling the function ifft, thereby recovering the original     *
+ * samples x.  Finally, the calculated samples X are saved to a specified     *
+ * file, if desired.                                                          *
+ ******************************************************************************/
+
+#include <stdio.h>
+#include <time.h>
+#include <stdlib.h>
+#include <string.h>
+#include <sys/time.h>
+#include "fft.c"
+#include "sys/types.h"
+#include "sys/sysinfo.h"
+
+
+double second()
+{
+        struct timeval tp;
+        struct timezone tzp;
+        int i = gettimeofday(&tp,&tzp);
+        return ( (double) tp.tv_sec + (double) tp.tv_usec * 1.e-6 );
+}
+
+
+int main(int argc, char **argv)
+{
+  int i;                    /* generic index */
+  char file[FILENAME_MAX];  /* name of data file */
+  int N;                    /* number of points in FFT */
+  double (*x)[2];           /* pointer to time-domain samples */
+  double (*X)[2];           /* pointer to frequency-domain samples */
+  double dummy;             /* scratch variable */
+  FILE *fp;                 /* file pointer */
+  double  t0, t1; /* time_t is defined on <bits/types.h> as long */
[…]

### 2012-07-23 benchmark/fft/submit.pl

@@ -1,0 +1,40 @@
+#!/usr/bin/perl -w
+
+$executable="fft_benchmark";
+$numproc=2;
+
+#Compile the source
+system("make");
+
+        # submit job
+        $cmd = "qsub -cwd -pe orte $numProc $executable.sge";
+        print $cmd."\n";
+
+        my $ret = `$cmd`;
+        die "Error: $?" if($? != 0);
+
+        chomp($ret);
+        my @words = split(/ /,$ret);
+        my $jobId = $words[2];
+
+        print "Job ID: $jobId submitted for $numProc processes\n";
+
+        #check queue
+        while(1)
+        {
+                my $line = "";
+
+                open(QUEUE,"qstat | grep $jobId |") or die "Unable to run qstat";
+                while(<QUEUE>)
+                {
+                        chomp;
+                        $line = $_;
+                }
+                close QUEUE;
+
+                last if($line eq "");
+                sleep(2);
+        }
+
+        print "Job ID: $jobId completed $numProc processes\n";
+        my $file = "image.sge.o$jobId";

### 2012-07-23 benchmark/old/benchmark.cpp

@@ -1,0 +1,155 @@
+// matrixstats.cpp
+// Written by Drew Weitz
+// Last Modified: June 9, 2003
+
+// This program is intended to be a very basic introduction to MPI programming.
+// For informationa bout each specific function call, consult the man pages
+// available on the cluster, or check out information available online at
+// www.iitk.ac.in/cc/param/mpi_calls.html
+
+// to include the MPI function library
+
+#include "mpi.h"
+#include <stdio.h>
+#include <string>
+
+int main (int argc, char *argv[]) {
+
+	// these variables will hold MPI specific information.
+	// numprocs will store the total number of processors allocated
+	// for the program run; myrank will store each individual procssors
+	// number assigned by the master.
+
+	int numprocs, myrank;
+
+	// In general, all nodes have a copy of all the variables defined.
+
+	// MPI_Init prepares the program run to communicate between all the
+	// nodes.  It is necessary to have this function call in all MPI
+	// code.
+
+	MPI_Init(&argc, &argv);
+
+	// MPI_Comm_size initializes the numprocs variable to be the number
+	// of processors alloocated to the program run.  MPI_COMM_WORLD is
+	// a macro that MPI uses to address the correct MPI netowrk.  Since
+	// multiple MPI jobs could be running at once, we want to have a way
+	// of addressing only the processors in our program run (or our 
+	// "world").
+
+	MPI_Comm_size(MPI_COMM_WORLD, &numprocs);
+
+	// MPI_Comm_rank initializes each nodes myrank variable to be it's
+	// processor number.
+
+	MPI_Comm_rank(MPI_COMM_WORLD, &myrank);
+	
+	MPI_Status status;
+	char greeting[MPI_MAX_PROCESSOR_NAME + 80];
+
+	int thematrix[numprocs-1][numprocs-1];
+	int thecube[numprocs-1][numprocs-1][numprocs-1];
+	int resultmatrix[numprocs-1][numprocs-1];
+ 	int temp  = 0;	
+	if (myrank == 0) {
+
+		printf("Preparing the matrix...\n");
+
+		for (int i=0; i < numprocs-1; i++) {
+			for (int j=0; j < numprocs-1; j++) {
+				thematrix[i][j] = 0;
+			}
+		}
+
[…]

### 2012-07-23 environment/manager.py

@@ -84,7 +84,7 @@ def runBenchmark():
 	print "Hawki>>> Running Benchmark ..."
 	try:
 		process = subprocess.Popen("starcluster sshmaster --user "+username + " " + clustername +
-			" ./instructions.sh", shell=True, stdout=subprocess.PIPE, stderr=subprocess.STDOUT)
+			" ./submit.pl", shell=True, stdout=subprocess.PIPE, stderr=subprocess.STDOUT)
 		output,stderr = process.communicate()
 		status = process.poll()
 		print output

### 2012-08-03 benchmark/fft/fft_benchmark.c
Benchmarks and UI

@@ -1,3 +1,11 @@
+/*******************************
+
+Sample FFT micro benchmark program
+inputfile should be given as command line argument
+eg: ./benchmark data.txt
+
+*******************************/
+
 #include <stdio.h>
 #include <time.h>
 #include <stdlib.h>
@@ -5,37 +13,6 @@
 #include <sys/time.h>
 #include "fft.c"
 #include "sys/types.h"
-#include "sys/sysinfo.h"
-
-
-struct CpuInfo {
-	char vendor_id[50];
-	int family;
-	char model[50];
-	float freq;
-	char cache[20];
-};
-
-void cpuinfo()
-{
-	struct CpuInfo info = {"", 0, "", 0.0, ""};
-	
-	FILE *cpuInfo;
-	
-	if( ( (cpuInfo = fopen("/proc/cpuinfo", "rb")) == NULL ) ) {
-		printf("ERRORE! Impossibile aprire il file relativo alla CPU.");
-		}
-	else {
-		while (!feof(cpuInfo)) {
-			fread(&info, sizeof(struct CpuInfo), 1, cpuInfo);
-			
-			if(info.family !=0) {
-				printf("%s\n%d\n%s\n%.2f\n%s\n", info.vendor_id, info.family, info.model, info.freq, info.cache);
-				}
-			}
-		}
-}
-
 
 double second()
 {
@@ -50,6 +27,7 @@ int main(int argc, char **argv)
 {
   int i;                    /* generic index */
   char file[FILENAME_MAX];  /* name of data file */
+  char output[FILENAME_MAX];/* name of data file */
   int N;                    /* number of points in FFT */
   double (*x)[2];           /* pointer to time-domain samples */
   double (*X)[2];           /* pointer to frequency-domain samples */
@@ -57,13 +35,13 @@ int main(int argc, char **argv)
   FILE *fp;                 /* file pointer */
   double  t0, t1;	    /* wall time variables */
   clock_t c0, c1; /* clock_t is defined on <bits/types.h> as long */
-  struct sysinfo memInfo;
   char hostname[100];
 
   gethostname(hostname,100);
 //  cpuinfo();
   /* Get name of input file of time-domain samples x. */
-  strcpy(file, "data.txt");
+  strcpy(file, argv[1]);
+  strcpy(output, "output.txt");
 
[…]

### 2012-08-04 docs/dissertation/MSc-coursework.tex
docs

@@
 \begin{abstract}
-The switch to cloud computing significant advancement in the history of computing.
+Scientific computing unravel the mysteries of science by constructing mathematical models and numerical algorithms.
+This required massive computational power and High-Performance Computing (HPC) solutions like cluster and grid have been the answer for massive computing to these needs for a long time.
+These HPC solutions are hard and expensive to setup, maintain and use.
+\emph{Cloud computing} is a model of delivering the existing compute infrastructure where computation and storage can be dynamically provisioned on a pay as you go model.
+Using a vendor cloud service like Amazon Web Service (AWS) can significantly reduce the effort to access these on-demand high performance resources.
+
+In this work we create a platform to study how useful Amazon EC2 cloud computing can be for scientific applications. 
+We classify the applications based on the concept of computational \emph{motif}\cite{asanovic2008parallel}  
 \end{abstract}
@@
 \chapter{Introduction}
-Stating the problem and
 
@@
 \section{Cloud Computing}
+In 1960 John McCarthy predicted that "computation may someday be organised as a public utility".
+Availability of high  capacity networks and low cost hardware as well as the adoption of hardware virtualisation technology made this prediction come true.
+This delivery model enabled a large community of end-users to obtain computing and storage capacity on-demand.
 
@@
 \subsection{N-Body Methods}
-MD, About the dwarf and application types
-optimisation, n^2 and nlogn
+MD, About the dwarf and application types optimisation, n2 and nlogn
 Communication pattern!!!
@@
 
-{\underline}Discrete Fourier Transform
+{\underline Discrete Fourier Transform}
 The discrete Fourier transform of N complex points fk is defined as
-\begin{math}
-
-\end{math}
 
@@
 \chapter{Benchmarking  programs}
+\subsection{Spectral Methods}
+\subsection{N-body}
 
-\begin{thebibliography}{100}
-
-\bibitem{ref:lam} L.Lamport. {\em 1986 Latex User's Guide
-and Reference Manual.} Addison Wesley. pp242.
-
-\bibitem{ref:bloggs} F.Bloggs. {\em 1993 Latex Users do it
-in Environments} Int. Journal of Silly Findings. pp 23-29.
-
-\end{thebibliography}
+\bibliographystyle{plain}
+\bibliography{dissertation}
 

### 2012-08-06 environment/manager.py
user reports

@@ -145,8 +145,9 @@ def saveResults():
 		benchmarkid=0
 		instanceid=0
 		inputid=0
-	
-		db = MySQLdb.connect("localhost","root","amma123","ubuntu_hawki" )
+		
+		#hard coded for prototype
+		db = MySQLdb.connect("localhost","root","pass123","ubuntu_hawki" )
 	        cursor = db.cursor()
 		benchmarks = benchmark.split('/')
 	
@@ -185,8 +186,8 @@ def saveResults():
 			inputid=0
 	
 		#Insert into results table
-		sql = "INSERT INTO cx_results (`benchmarkid` , `instanceid` , `inputid` , `userid` , `timetocompletion`, `status`)\
-			 VALUES (%d, %d, %d, %d, %f , %d)" % (benchmarkid, instanceid, inputid, userid, timetocompletion, status)
+		sql = "INSERT INTO cx_results (`benchmarkid` , `instanceid` , `inputid` , `userid` , `size`, `timetocompletion`, `status`)\
+			 VALUES (%d, %d, %d, %d, %d, %f, %d)" % (benchmarkid, instanceid, inputid, userid, size, timetocompletion, status)
 		print sql
 		try:
 	   		cursor.execute(sql)

### 2012-08-06 docs/dissertation/MSc-coursework.tex

@@
 
-\chapter{Introduction}
+\section{Introduction}  
+In this dissertation, we are trying to prove that a live micro benchmark tool can be useful to cloud users to estimate 
+the time and cost of execution before putting significant initial efforts and skills to port the applications to the cloud infrastructure. 
+We also study the possibilities of classifying micro benchmarks based on 13 emph{motifs}\cite{} or patterns.  
+Our experiment uses two of these patterns, spectral methods and N-body simulation, to test the concept of live benchmark tool.
 
-\chapter{Background}
+\section{Cloud computing}  
+In 1960 John McCarthy predicted that "computation may someday be organised as a public utility" \cite {dikaiakos2009cloud}. 
+Availability of high capacity networks and low cost hardware as well as the adoption of hardware virtualisation technology 
+made this prediction come true. These technologies and delivery models called "cloud computing" enabled a large community of 
+end-users to obtain computing and storage capacity on-demand.  
+There are several aspects in cloud computing which makes it attractive to users. The most importan one is the illusion of 
+infinite computing resources on demand which reduces the user's effort to plan ahead for resource provisioning. 
+Another feature is that cloud computing allow users to start small in a test environment and grow bigger without any upfront 
+commitments to service providers. Finally, from a pricing point of view, provision to pay only for the computing, storage or network 
+resources that you use makes cloud a cost effective solution for users \cite {fox2009above}.
 
-\section{Cloud Computing}
-In 1960 John McCarthy predicted that "computation may someday be organised as a public utility".
-Availability of high  capacity networks and low cost hardware as well as the adoption of hardware virtualisation technology made this prediction come true.
-This delivery model enabled a large community of end-users to obtain computing and storage capacity on-demand.
+\subsection{HPC in the cloud}  
+Cloud computing started in context of web applications and enterprise systems that have completely different requirements 
+when compared to high performance computing applications like scientific computing. Traditionally these applications rely 
+on HPC centers with dedicated systems connected through high bandwidth interconnects and uses parallel file systems.   
+Cloud provides the ability to manage or modify the software environment and get on-demand access to virtual resources 
+which makes it attractive to HPC users. The cloud resources can be used to replace the existing systems or supplement them. 
+One good example is the cloud storage provided by
 
-\subsection{Why Cloud Computing?}
-\subsubsection{Resource on-demand}
-easy, accesibility
-\subsubsection{Pay as you go}
-\subsubsection{Maintenance and Upgradation}
-\subsubsection{Eco-friendly}
+http://science.energy.gov/~/media/ascr/pdf/program-documents/docs/Magellan_Final_Report.pdf
 
-\subsection{Cloud Computing service models}
+Introduction Paragraph, comparison with Clusters  
+\subsection{Advantages}  
+\subsection{Limitation}  
+Network Limitations, Availability, Stability of performance  
+Benifits
+
+\subsection{Cloud Computing Deployment models}  
+A cloud being a data center hardware and software can be deployed in several ways depending on several aspects like cost effectiveness, privacy and security.
+The four deployment models of cloud computing are:
+
+\underline{ Public Cloud}  
+When the cloud is available to the general public in a pay as you go manner, it is called a public cloud. 
+Public cloud infrastructure is owned and maintained by vendors that can support very large infrastructure and hence they are also known as vendor clouds. 
+Amazon Web Services\cite{} which is studied in this project would fall in this category. 
+Some of the other major companies offering cloud services are Rackspace\cite{}, Microsoft\cite{} and Google\cite{}. 
+Typically, end-users registered for this service using a credit card and they are provided access to this cloud infrastructure via internet.
+
+\underline{Private Cloud}  
+A cloud infrastructure operating for a single organisation is a private cloud. This can be managed by the organisation or by a third party. 
+Typically a private cloud is hosted within the organisation network but they can also be hosted externally. 
+To provide virtualisation to users cloud software stacks like OpenNebula, Eucalyptus and Openstack are used. 
+Private cloud provides most of the benefits of public clouds while avoiding the issues concerning security of data and performance of public clouds. 
+Even though the organisation have to setup and manage the infrastructure,  it can be less expensive than public clouds\cite{Magellan_Final_Report.pdf}.
+
+\underline{ Community Cloud}  
+When a private cloud infrastructure is deployed by two or more organisations having similar requirements, it becomes a community cloud. 
+The cost of operating the cloud is shared by the organisations in the community. 
+Cost need to directly translate to currency in a community cloud, it can be credits based or fixed usage based on the agreement between the organisations.
+
+\underline{Hybrid Cloud}  
+To benefit from the advantages of multiple deployment models, the two or more cloud infrastructures can be bound together to form a hybrid cloud.
+It requires onsite resources accessible without internet that provides flexibility and remote server based infrastructure to provide scalability.
+Hybrid clouds can be very useful with the implementing concepts like cloud bursting where the software application running on an internal organisational cloud is dynamically ported to a public cloud to address the increase in resource demand.
+To enable portability of applications in hybrid model, the independent infrastructures should be technology compliant.
+
+\subsection{Cloud computing service models}  
+Cloud computing   
 \subsubsection{IaaS}  
@@
 \subsubsection{Saas}
-
-\subsection{Cloud Computing Deployment models}
-\subsubsection{Private Cloud}
-\subsubsection{Public Cloud}
-\subsubsection{Hybrid Cloud}
-\subsubsection{Community Cloud}
 
@@
 \subsubsection{EC2 cluster compute}  
-
-\section{HPC in the cloud}
-Introduction Paragraph, comparison with Clusters
-\subsection{Advantages}
-\subsection{Limitation}
-Network Limitations, Availability, Stability of performance
-Benifits
 \subsection{Amazon Cluster compute}  
-
 \section{Parallel Applications and 13 Dwarfs}  
 Explain the 13 dwarfs and under the two sections explain N-body and FFT  
-
 \subsection{N-Body Methods}  
@@
 Communication pattern!!!  
-
 \subsection{Spectral Methods}  
 In scientific computing, a class of techniques used to numerically solve differential equations involving the use of Fast Fouries Transform are called spectral methods  
-
 Fourier transform  
@@
 – Optics   
-
 • Numerical analysis   
@@
 – Large integer multiplication (Prime finding)   
-
 • Statistics   
@@
 – Probability theory  
-
 {\underline Discrete Fourier Transform}  
 The discrete Fourier transform of N complex points fk is defined as   
-
 Communication pattern!!!

### 2012-08-07 benchmark/pingpong/benchmark.c
benchmark manager

@@ -1,0 +1,118 @@
+/*******************************
+Sample benchmark program
+*******************************/
+
+#include <stdlib.h>
+#include <stdio.h>
+#include <mpi.h>
+
+int main(int argc, char* argv[]){
+  int rank, size, numiter,length;
+  int start,stop,i,iter;
+  int tag1, tag2,extent;
+  double *sbuffer;
+  double t1, t2,totmess;
+  MPI_Comm comm;
+  MPI_Status status;
+
+  comm  = MPI_COMM_WORLD;
+  tag1= 1;
+  tag2 = 2;
+
+  MPI_Init(&argc, &argv);
+  MPI_Comm_rank(comm, &rank);            
+  MPI_Comm_size(comm, &size); 
+
+  // Abort if run on less than 2 processors.
+  if(size < 2){
+    if(rank == 0){
+      printf("The code must be run on at least 2 processors.\n");
+    }
+    MPI_Finalize();
+    exit(1);
+  }
+  
+  if(argc < 2) {
+    if(rank == 0){
+     printf("Code requires 2 input arguments: The array length and the number of iterations. \n");
+    }
+    MPI_Finalize();
+  exit(1);
+  }
+
+  if(rank > 1){
+    printf( "Rank %d not participating \n",rank);
+  }
+
+  if (rank == 0) {
+    length = atoi(argv[1]);
+    numiter = atoi(argv[2]);
+    printf("Array length = %d , number of iterations = %d\n",length,numiter);
+  }
+
+  MPI_Bcast(&length,1,MPI_INT,0,comm);
+  MPI_Bcast(&numiter,1,MPI_INT,0,comm);
+
+
+  // Allocate array
+  sbuffer = malloc(length*sizeof(double));
+ 
+  // Send 'buffer' back and forth between rank 0 and rank 1.
+  for(i=0;i<length;i++)
+    sbuffer[i] = (double)rank + 10.0;
+
+  // Time the parallel execution.
+  MPI_Barrier(comm);
+  t1 = MPI_Wtime();
+
+  // Swap back and forth for iter times
+
+  for(iter=1;iter<numiter;iter++){
+
+  if(rank == 0){
+
+  // Timings only make sense when no print statements are includes!
+
+   MPI_Ssend(&sbuffer[0],length,MPI_DOUBLE,1,tag1,comm);
+   MPI_Recv(&sbuffer[0],length,MPI_DOUBLE,1,tag2,comm,&status);
[…]

### 2012-08-07 environment/manager.py

@@ -126,9 +126,10 @@ def saveResults():
 		output = {}	#empty array to store results
 		outputfile = open(results+"/benchmark.sge.o1",'r')	#read file
 		x = outputfile.readline()
-		status=1
+		status=0
 		timetocompletion = 0.0
 		while (x):
+			print x+"<br>"
 			var = x.split(' ')
 			if (var[0]=='real'):
 				timetocompletion = float(var[-1])
@@ -227,6 +228,6 @@ runBenchmark()
 getResults() #readtime computation time writetime memoryused cpuused
 if(archive):
 	saveResults()
-terminateCluster()
+#terminateCluster()
 
 #End

### 2012-08-08 docs/dissertation/MSc-coursework.tex
Implementation outline

@@
 These HPC solutions are hard and expensive to setup, maintain and use. 
-\emph{Cloud computing} is a model of delivering the existing compute infrastructure where computation and storage can be dynamically provisioned on a pay as you go model.
+\emph{Cloud computing} is a model of delivering the compute infrastructure in which 
+computation and storage can be dynamically provisioned on a pay as you go model. 
 Using a vendor cloud service like Amazon Web Service (AWS) can significantly reduce the effort to access these on-demand high performance resources.
@@
 
-\section{Cloud computing}  
+\chapter{Background}
+
+\section{Cloud computing}  %one page about cloud computing
 In 1960 John McCarthy predicted that "computation may someday be organised as a public utility" \cite {dikaiakos2009cloud}. 
-Availability of high capacity networks and low cost hardware as well as the adoption of hardware virtualisation technology 
+Availability of high capacity networks and low cost hardware as well as the adoption of hardware virtualisation\cite{} technology 
 made this prediction come true. These technologies and delivery models called "cloud computing" enabled a large community of 
 end-users to obtain computing and storage capacity on-demand.
+
 There are several aspects in cloud computing which makes it attractive to users. The most importan one is the illusion of 
@@
 commitments to service providers. Finally, from a pricing point of view, provision to pay only for the computing, storage or network 
-resources that you use makes cloud a cost effective solution for users \cite {fox2009above}.
+resources that you use makes cloud a cost effective solution for users \cite {armbrust2010view}.
 
-\subsection{HPC in the cloud}  
+\subsection{HPC in cloud}  %one page about hpc in cloud with examples like cern
 Cloud computing started in context of web applications and enterprise systems that have completely different requirements 
-when compared to high performance computing applications like scientific computing. Traditionally these applications rely 
+when compared to high performance computing (HPC) applications like scientific computing. Traditionally these applications rely 
 on HPC centers with dedicated systems connected through high bandwidth interconnects and uses parallel file systems.   
-Cloud provides the ability to manage or modify the software environment and get on-demand access to virtual resources 
-which makes it attractive to HPC users. The cloud resources can be used to replace the existing systems or supplement them. 
-One good example is the cloud storage provided by
+Cloud provides the ability to manage or modify the software environment and get on-demand access to virtual resources which makes it attractive to HPC users. 
+The cloud resources can be used to replace the existing systems or supplement them. 
+One good example is the cloud storage provided by ........
 
-http://science.energy.gov/~/media/ascr/pdf/program-documents/docs/Magellan_Final_Report.pdf
-
+%http://science.energy.gov/~/media/ascr/pdf/program-documents/docs/Magellan_Final_Report.pdf  
 Introduction Paragraph, comparison with Clusters 
-\subsection{Advantages}  
-\subsection{Limitation}  
 Network Limitations, Availability, Stability of performance  
@@
 A cloud being a data center hardware and software can be deployed in several ways depending on several aspects like cost effectiveness, privacy and security.
-The four deployment models of cloud computing are:
+Four deployment models of cloud computing are:
 
@@
 Typically a private cloud is hosted within the organisation network but they can also be hosted externally. 
-To provide virtualisation to users cloud software stacks like OpenNebula, Eucalyptus and Openstack are used. 
+To provide virtualisation to users cloud software stacks like OpenNebula\cite{}, Eucalyptus\cite{} and Openstack\cite{} are used. 
 Private cloud provides most of the benefits of public clouds while avoiding the issues concerning security of data and performance of public clouds. 
@@
 
-\underline{ Community Cloud}  
+\underline{Community Cloud}
 When a private cloud infrastructure is deployed by two or more organisations having similar requirements, it becomes a community cloud. 
 The cost of operating the cloud is shared by the organisations in the community. 
-Cost need to directly translate to currency in a community cloud, it can be credits based or fixed usage based on the agreement between the organisations.
+In community cloud, cost need not directly translate to currency in a community cloud.
+Usage can be credits based or fixed usage based on the agreement between the organisations.
 
@@
 It requires onsite resources accessible without internet that provides flexibility and remote server based infrastructure to provide scalability. 
-Hybrid clouds can be very useful with the implementing concepts like cloud bursting where the software application running on an internal organisational cloud is dynamically ported to a public cloud to address the increase in resource demand.
+Hybrid clouds can be very useful with the implementing concepts like cloud bursting\cite{}. 
+The software application running on an internal organisational cloud is dynamically ported to a public cloud to address the increase in resource demand.
 To enable portability of applications in hybrid model, the independent infrastructures should be technology compliant.
@@
 \subsection{Cloud computing service models}
-Cloud computing   
-\subsubsection{IaaS}  
-\subsubsection{PaaS}  
-\subsubsection{Saas}
 
-\section{Amazon Web Service}  
+Cloud computing services are normally categorized as Software as a Service (SaaS), Platform as a Service (PaaS) and Infrastructure as a Service (IaaS).
+high performance computing can significantly utilise each of these models.
+The difference between the service models is based on the abstraction level at which the service is provided to the
+end user. The end user have the freedom to customise the applications and environment above the abstracted level. 
+For example, in IaaS, a virtual hardware is provided to the end user and the user then decides on the operating system and applications to be installed on the system. 
+We will discuss each of these service models with existing examples in the public clouds to understand their features.
+
+\subsubsection{Infrastructure as a Service}
+
+In Infrastructure as a Service service model, cloud provides virtual equipments including hardware, storage and networking components. 
+The service provider is responsible for creating, running, and maintaining it. 
+In public cloud, the client typically pays on a per-use basis for use of the equipment.
+
+Today, the most widely used IaaS provider is Amazon Web Services. Amazon provides different types if Infrastructures for different pricing. 
+Amazon Simple Storage Service (S3) and Elastic Block Storage (EBS) are methods of data storage. 
+Being a key-based storage which is highly scalable, Amazon S3 is capable of handling data integrity and fault tolerance. 
+Amazon EBS storage provides virtual block storage devices that can easily be associated with elastic compute instances to persistantly store data. 
+S3 charges for the amount of data transferred to and from the device and the number of metadata operations performed. 
+Both EBS and S3 charges for data stored per month, but there is no charge for data transferred within an Availability Zone\cite{}.
+Data transferred between EC2 instances and S3 located in different Availability Zones in the same region will be charged Regional Data Transfer and 
+data transferred between devices in different regions will be charged on both sides of transfer as Internet Data Transfer.
+
+Eucalyptus, OpenNebula and OpenStack are open source software packages that can be used to create a private cloud Infrastructure service.
+Most of the services provided by AWS including machine image management, persistent storage etc are provided by these packages. 
+They often provide interfaces similar to vendor clouds like Amazon EC2 which allow the use of same set of tools and methods.
+
+\subsubsection{Platform as a Service}
+
+Platform as a Service (PaaS) helps in building and delivering applications by providing a computing platform. 
+It includes facilities for different phases of a project lifecycle including design development, deployment and testing.
+Windows Azure is a good example of a popular PaaS service. 
+Azure provides an environment for development, hosting, and management of applications.
+Applications hosted in Azure platform are provided compute resources and storage on-demand.
+Azure has two virtual machine instance types: the webrole instance and the worker role instance. 
+To store data and access it from these virtual machines Azure provides Blob storage Service.
+
+Even though Azure platform is designed for web applications, its use for HPC applications is being explored \cite{li2010escience}.
+
+\subsubsection{Software as a Service}
+
+Software as a Service (SaaS) provides end users with direct access to an application with a specific function. 
+Applications and related data are centrally hosted in the cloud and accessed via a web browser.
+
+Examples in the public clouds include services like Google drive\cite{} and Microsoft Skydrive\cite{}.
+Documents, images, spreadsheets and presentations can be created and imported using a web interface. 
+Both of these services provide desktop application plugins to synchronise data created using the software suits like Microsoft Office. 
+This gives users the convenience of accessing their application data from any workstation or mobile device.
+
+\section{Amazon Web Services}  
+In 2006, Amazon.com\cite{} started offering a collection of cloud computing services over the internet.
+This collection of web services is called Amazon Web Services.
+Today, Amazon Web Services provides an IT infrastructure platform for business in the cloud with data center locations in the U.S., Europe, Brazil, South America, Singapore, and Japan.
+
+\subsection{Amazon EC2}  
+Amazon Elastic Compute Cloud (Amazon EC2) is an IaaS that provides resizable or elastic compute capacity in the cloud.
+It is designed to provide the freedom of choosing development environment and software stack to the developers.
+Amazon EC2’s web service interface allows users to launch and configure capacity with minimal effort.
+The time required to launch a new instance is less than a few minutes allowing users to quickly increase or decrease capacity, as their computing requirements change.
+
 \subsection{Amazon Machine Instance}
+An Amazon Machine Image (AMI) is a pre-configured template operating system which is used to launch an EC2 instance. Users can create their custom AMI usind the developer tools. 
+A machine image is compressed and split into a set of 10MB chunks and stored in Amazon S3 storage.
+Even though each AMI has a pointer to a default kernel, user may choose a kernel from a list of compatible kernels maintained by Amazon and its partners like Redhat and Canonical.
+
 \subsection{Types of Instances}
-\subsection{Amazon EC2}  
-different instances chart and limitations of microinstance.  
+
+image{}
+
 \subsubsection{EC2 cluster compute}
-\subsection{Amazon Cluster compute}  
+
 \section{Parallel Applications and 13 Dwarfs}  
@@
 
-\chapter{Live Benchmark Tool Setup}
-\section{System Design}
-\subsection{Architecture}
-\subsection{Sequence diagram}
-\subsection{Database Design}
+Hawk-i Live Benchmark Tool Setup
 
-\section{Instance types Used}
-Refer to graph in Background
-Why these types?
-\section{Sun Grid Engine Cluster}
-Why sungrid Engine
-\section{SGE Clustering in Amazon cloud}
-  benchmark to show how cluster instances are faster than normal high cpu instances
-\section{Web interface}
+Design Decisions and Assumptions
+Instances used
+AWS provides several EC2 Instances [figure: Refer to graph in Background]. Features of these instances were carefully studied and the following instances were selected to be included in Hawk-i tool. 
+Standard instances: m1.small, m1.medium, m1.large, m1.xlarge
+High memory instances: m2.xlarge, m2.2xlarge, m2.4xlarge
+High CPU instances: c1.medium, c1.xlarge
+Cluster Compute instances: cc1.4xlarge, cc2.8xlarge (Requires different AMI)
+Excluded: 
+t1.micro (What was seen observed during initial experiments)
+cg1.4xlarge (Added complexity)
+AMI used
+The AMI used for this experiment is an Ubuntu image with pre-configured sun grid engine and OpenMPI.
+For this project we use two custom AMIs [Appendix], Ubuntu instance for clustering of normal instances and CentOS instance for Cluster compute.
+Sun Grid Engine
+We selected Sun Grid Engine (SGE) as the batch queuing system due to my previous experience in building bare metal heterogeneous cluster using sun grid engine and familiarity of using Ness[].
+In virtual environment the installation and configuration was no different from the actual cluster building.
+Starcluster
+Starcluster is a MIT cluster management tool [] to manage the SGE cluster. Hawki use Starcluster command line tools to    
+System interface
+In the initial design there are two interfaces to the Hawki system, a command line interface to add and schedule benchmarks and a web interface to view the results.
+Scheduled execution cost of the system was too high.
+Hence we thought of an alternative on-demand benchmark using the web interface.
+We still retain the scheduled benchmark on a small instance to verify the stability of results provided by AWS.
+Due to convenience of scripting and wide library availability, Python was decided to be used for creating the command line interface.
+Python being pre-installed in almost all major Linux distribution made this decision easier.
+The web interface is developed using PHP, MySQL and Apache.
+These applications are free and opensource under GPL License.
+Web server was configured and the application was deployed in Manager Instance.
+Joomla Content Management system is used for User Management and Navigation.
+Benchmarks used
+To test the functionality of this tool, the initial plan was to create micro benchmarks mimicking the execution behaviour of existing real life HPC applications.
+On further research we found a study by University of Berkley [] to classify of benchmarks based on the computation pattern.
+This approach was taken for selecting benchmarks to be added in Hawki.
+The option to add new benchmarks was decided to be provided for future use.
+
+System Design
+In this Section, we discuss the design of Hawki system. 
+Architecture
+Entire Hawki system was divided into three different subsystems named Manager Environment, Benchmarks, and Web Interface.
+Manager Environment
+Python scripting to handle command execution request from the web interface. It accepts command line input from the manager instance. 
+Benchmark
+FFT and MD code was used as sample benchmark to test the system. Ping pong is also used to test the communication performance of the cluster.
+Web Interface
+Web interface provides Hawki tool access for normal users, managers and administrator.
+Normal users will view the stability of execution of different benchmarks over a large period of time.
+Managers have the option to select and run benchmarks and view the history of all their execution as reports.
+Administrator has full privilege in the system and they add, edit and remove benchmarks, input types and instances.
+ 
+Sequence diagram
+The data transfer between different subsystems is shown in figure []
+
+Database Design
+All results from executing benchmark is stored in a database and the users have the option to view their benchmarks at any point of time.
+
+Implementation
+In this section we discuss the implementation strategies used to develop and test Hawki tool.
+
+Manager environment
+Hawki provides command line interface from the manager instance.
+The administrator can test the programs and debug Hawki using this interface.
+This is a python manager script that manages different benchmarks.
+
+Benchmarks
+FFT and MD are the benchmarks. Ping pong was used to test the message passing capacity.
+Results obtained
+
+Web interface
+
+Web interface
 Describe in detail
-\subsection{Admin panel}
-\subsection{User Dashboard}
+Admin panel
+subsectionUser Dashboard
 
@@
 
-\chapter{Cluster Computing Setup}
-\subsection{Using Starcluster}
-\subsection{Cluster Management package}
-\subsection{Using Sun Grid Engine}
-\subsection{Creating Dashboard}
-\chapter{Benchmarking  programs}
-\subsection{Spectral Methods}
-\subsection{N-body}
-
 \bibliographystyle{plain}
